\name: A hierarchical Bayesian model for Supernova Cosmology

### 2017-09-21 papers/methods/paper.tex
Paper updates

The underlying actual supernova population is not as clear cut, and indeed accurately characterising this population, its evolution over redshift and effects from environment is one of the challenges of supernova cosmology. However, given some modelled underlying population that lives in the redshift dependent space $M_B$, $x_1$ and $c$, the introduction of cosmology into the model is simple -- it is encoded in the functional map between those two populations, from apparent magnitude space to absolute magnitude. Specifically, for any given supernova our functional map may take the traditional form:
\begin{equation}
M_B = m_B + \alpha x_1 - \beta c - \mu(z) + \text{corrections},
\end{equation}
where $\alpha$ is the stretch correction \citep{Phillips1993}, and $\beta$ is the colour correction \citep{Tripp1998} that respectively encapsulate the empirical relation that broader and bluer supernovae are brighter. The $\text{corrections}$ term at the end often includes corrections for host galaxy environment, as this has statistically significant effects on supernova properties \citep{Kelly2010,Sullivan2010,Rigault2013,Uddin2017}. The cosmological term, $\mu(z)$ represents the distance modulus, and is precisely known given cosmological parameters and an input redshift.

>>>>

The underlying actual supernova population is not as clear cut, and indeed accurately characterising this population, its evolution over redshift and effects from environment is one of the challenges of supernova cosmology. However, given some modelled underlying population that lives in the redshift dependent space $M_B$, $x_1$ and $c$, the introduction of cosmology into the model is simple -- it is encoded in the functional map between those two populations, from apparent magnitude space to absolute magnitude. Specifically, for any given supernova our functional map may take the traditional form:
\begin{equation}
M_B = m_B + \alpha x_1 - \beta c - \mu(z) + \text{corrections},
\end{equation}
where $\alpha$ is the stretch correction \citep{Phillips1993}, and $\beta$ is the colour correction \citep{Tripp1998} that respectively encapsulate the empirical relation that broader and bluer supernovae are brighter. The $\text{corrections}$ term at the end often includes corrections for host galaxy environment, as this has statistically significant effects on supernova properties \citep{Kelly2010, Lampeitl2010, Sullivan2010, Rigault2013, Uddin2017}. The cosmological term, $\mu(z)$ represents the distance modulus, and is precisely known given cosmological parameters and an input redshift.

For traditional $\chi^2$ analyses such as that found in \citet{Kowalski2008, Conley2011, Betoule2014}, minimise the difference in distance modulus between the cosmologically predicted values $\mu_C$ and the observed distance modulus $\mu_{\rm obs}$, shown respectively below:
\begin{align}
\mu_C &= 5 \log\left[ \frac{(1+z)\chi}{10} \right]\\
&=\\
\mu_{\rm obs} &= m_B + \alpha x_1 - \beta c - M_B
\end{align}
